\documentclass[10pt,journal,compsoc]{IEEEtran}

\pdfminorversion=7

\usepackage{amsmath,amsfonts}
\usepackage{algorithmic}
\usepackage{array}
\usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
\usepackage{textcomp}
\usepackage{stfloats}
\usepackage{url}
\usepackage{verbatim}
\usepackage{graphicx}


\usepackage{enumerate}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{xspace}
\usepackage{balance}
\usepackage[most]{tcolorbox}
\usepackage{awesomebox}
\usepackage{multirow}
\usepackage{blindtext}



\hyphenation{op-tical net-works semi-conduc-tor IEEE-Xplore}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.15emX}}

%.1667


% Custom colors
\definecolor{keywords}{rgb}{0.5,0,0.35}
\definecolor{comments}{RGB}{0,0,113}
\definecolor{red}{RGB}{160,0,0}
\definecolor{green}{RGB}{0,150,0}
 
\lstset{language=Python, 
        basicstyle=\ttfamily\small, 
        keywordstyle=\color{keywords}\bfseries,
        commentstyle=\color{comments},
        stringstyle=\color{red},
        showstringspaces=false,
        %identifierstyle=\color{red},
       }
       


% Pictures
\usepackage{graphicx}       



\newtcbtheorem{obs}{Finding}{%
        theorem name,%
        colback=gray!5,%
        colframe=gray!35!black,%
        fonttitle=\bfseries,title after break={Lemma  -- \raggedleft Continued}%
    }{lem}

\newcommand{\tb}[2]{\tipbox{{\bf Finding #1}. #2}}

\newcommand{\droidxp}{DroidXP\xspace}
\newcommand{\review}[1]{\textcolor{blue}{#1}}
\newcommand{\alert}[1]{\textcolor{red}{#1}}
\newcommand\kn[1]{\textcolor{red}{KN: #1}}
\newcommand\fh[1]{\textcolor{green}{FH: #1}}
\newcommand\rb[1]{(\textcolor{blue}{RB: #1})}

\newcommand{\highlight}[1]{{\color{red}}#1}

\newcommand\raw[1]{\textcolor{red}{#1}\xspace}

\newcommand{\mas}{MAS approach\xspace}

\newcommand{\fm}[1]{\emph{#1}\xspace}

\newcommand{\gps}{\fm{gappusin}\xspace}  % the gappusin family.

\newcommand{\sscore}{Similarity Score\xspace}

\newcommand{\rqa}{What is the impact of considering a larger and diverse dataset on the accuracy of the \mas for malware classification?}

\newcommand{\rqb}{How much gain we obtain on the performance of the \mas for malware classification when considering trace analysis?}

\newcommand{\rqc}{What is the influence of the similarity between the original and repackaged
                  versions of the apps on the performance of the \mas for malware classification?}

\newcommand{\rqd}{What is the influence of the malware family (e.g., \fm{gappusin}, \fm{kuguo}, \fm{dowgin}) on the performance of the \mas for malware classification?}

\newcommand{\rqe}{How much gain we obtain on the performance of the \mas for malware classification when considering its extensions?}


\newcommand{\repack}{RePack\xspace}
\newcommand{\amc}{AndroMalPack\xspace}

\newcommand{\appsSmall}{102\xspace}
\newcommand{\apps}{\textcolor{blue}{4,076}\xspace}
\newcommand{\napps}{\textcolor{blue}{726}\xspace}

\newcommand{\sds}{\texttt{SmallDS}\xspace}
\newcommand{\cds}{\texttt{LargeDS}\xspace}
\newcommand{\nds}{\texttt{DS3}\xspace}
\newcommand{\avt}{\texttt{avclass2} tool\xspace}
\newcommand{\vt}{\texttt{VirusTotal}\xspace}
\newcommand{\se}{security engine\xspace}
\newcommand{\ses}{security engines\xspace}


\newcommand{\fone}{F1-score\xspace}
\newcommand{\fscoreSmall}{0.89\xspace}
\newcommand{\fscoreNew}{0.85\xspace}

\newcommand{\nfscoreSmall}{0.85\xspace}
\newcommand{\nfscoreSmallC}{0.87\xspace}

\newcommand{\fscore}{\textcolor{blue}{0.59}\xspace}
\newcommand{\fscoreC}{\textcolor{blue}{0.49}\xspace}

\newcommand{\malwares}{\textcolor{blue}{2,729}\xspace}
\newcommand{\malwaresP}{\textcolor{blue}{66.95}}
\newcommand{\malwaresN}{\textcolor{blue}{87.98}}
\newcommand{\appsGps}{\textcolor{blue}{1,337}\xspace}
\newcommand{\appsGpsFN}{\textcolor{blue}{1,025}\xspace}



\begin{document}

\title{The Achilles' Heel of the Android Mining Sandbox Approach for Malware Identification}


\author{Francisco Costa, %~\IEEEmembership{Member,~IEEE,}
        Ismael Medeiros, %~\IEEEmembership{Fellow,~OSA,}
        Leandro Oliveira, %~\IEEEmembership{Fellow,~OSA,}
        Jo\~{a}o Cal\'{a}ssio, %~\IEEEmembership{Fellow,~OSA,}
        Rodrigo~Bonif\'{a}cio,
        Krishna Narasimhan,
        Mira Mezini,
        and M\'{a}rcio Ribeiro% <-this % stops a space
\IEEEcompsocitemizethanks{
\IEEEcompsocthanksitem F. Costa, I. Medeiros, L. Oliveira, J. Cal\'{a}ssio, and R. Bonif\'{a}cio are with the 
Computer Science Department, University of Bras\'{i}lia, Bras\'{i}lia, Brazil.
E-mail: \{francisco.costa,ismael.medeiros,leandro.oliveira,joao.calassion\}@aluno.unb.br and \{rbonifacio\}@unb.br.
\IEEEcompsocthanksitem K. Narasimhan and M. Mezini are with the Software Technology Group / TU Darmstadt, Darmstadt, Germany.\protect\\
E-mail: \{kri.nara,mezini\}@informatik.tu-darmstadt.de.
\IEEEcompsocthanksitem M\'{a}rcio Ribeiro is with the Computing Institute, Federal University of Alagoas, Macei\'{o}, Brazil\protect\\
E-mail: marcio@ic.ufal.br}% <-this % stops an unwanted space
%\thanks{Manuscript received April 19, 2005; revised August 26, 2015.}
}



% \thanks{}



%\author{IEEE Publication Technology Department

%\author[1]{Francisco Handrick da Costa}
%\author[1]{Ismael Medeiros}
%\author[1]{Thales Menezes}
%\author[1]{Jo\~{a}o Victor da Silva}
%\author[1]{Ingrid Lorraine da Silva}
%\author[1]{Rodrigo Bonif\'{a}cio}
%\author[2]{Krishna Narasimhan}
%\author[3]{M\'{a}rcio Ribeiro}

%\address[1]{Computer Science Department, University of Bras\'{i}lia, Brazil}
%\address[2]{Software Technology Group, TU Darmstadt, Germany}
%\address[3]{Institute of Computing, Federal University of Alagoas, Brazil}

\input{abstract}


\markboth{IEEE Transactions on Software Engineering,~Vol.~XX, No.~X, August~XXXX}%
         {Costa \MakeLowercase{\textit{et al.}}: The Achilles' Heel of the Android Mining Sandbox Approach}


\maketitle


\begin{IEEEkeywords}
Android Malware Detection, Dynamic Analysis, Mining Android Sandboxes.
\end{IEEEkeywords}

\input{introduction}
\input{background}
\input{experimentalSetup}
\input{results}
\input{complementary}
%\input{newDataset}
\input{discussion}
\input{conclusions}
\balance 

\bibliographystyle{IEEEtran}
\bibliography{ref}








\end{document}


